### 2021-07-08 doc/thesis/chapters/dsp.tex
new diagrams

In order to achieve this, the incoming signal needs to be multiplicated with a carrier signal, that is generated locally in the receiver, by a local oscillator (LO).
Depending on the frequency $f_{LO}$ of this local carrier, the resulting signal will be shifted to baseband, or an IF.

@@

\includepicture [1.0] [0] {Block diagram and signal spectrum of down-conversion.} {bd_down_conversion_spectrum} {img/draw.io/down-conversion-AM-spectrum-and-bd}

@@

\includepicture [1.0] [0] {Signal spectrum, explaining the process of down-conversion.} {down_conversion_spectrum_steps} {img/down-conversion-AM-dsb-sc}

>>>>

In order to achieve this, the incoming signal needs to be multiplicated with a carrier signal, that is generated locally in the receiver, by a local oscillator (LO).
Depending on the frequency $f_{LO}$ of this local carrier, the resulting signal will be shifted to baseband, or an IF.
Note, that in the case of down-conversion, the local oscillator frequency $f_{LO}$ is interchangeably denoted as carrier frequency $f_c$.

@@

\includepicture [1.3] [0] {Block diagram and signal spectrum of down-conversion.} {bd_down_conversion_spectrum} {img/draw.io/down-conversion-AM-spectrum-and-bd}

@@

\includepicture [1.0] [0] {Signal spectrum, explaining the process of down-conversion.} {down_conversion_spectrum_steps} {img/draw.io/down-conversion-steps-AM-spectrum}
